Statistics for HIV surveillance

### 2021-09-29 docs/24-09-21_new-cohort/new-cohort.Rmd
This was in September not August

---
title: "Statistics for HIV surveillance"
author: "Adam Howes"
date: "August 2021"
output:
  beamer_presentation:
    latex_engine: pdflatex
    highlight: haddock
    fig_width: 7
    fig_height: 3
    includes:
      in_header: preamble.tex
  slidy_presentation:
    highlight: haddock
subtitle: StatML Kick-off Camp
bibliography: citations.bib
institute: Imperial College London
---

>>>>

---
title: "Statistics for HIV surveillance"
author: "Adam Howes"
date: "September 2021"
output:
  beamer_presentation:
    latex_engine: pdflatex
    highlight: haddock
    fig_width: 7
    fig_height: 3
    includes:
      in_header: preamble.tex
  slidy_presentation:
    highlight: haddock
subtitle: StatML Kick-off Camp
bibliography: citations.bib
institute: Imperial College London
---
